### 2014-02-27 paper/formal.tex
more + fix erasure function

\section{Security Guarantees}
\label{sec:formal}

In this section we present the formal security guarantees provided by
our embedding.
%
Specifically, we show that a combined langauge, |specLang alpha
(targetLang nop)|, satisfies a form of non-interference.
%
Intuitively, non-interference states that secret values cannot be
leaked by programs written in the language.

In this section, we show that LIO computations satisfy
termination-sensitive non-interference. As in ~\cite{Li+:2010:arrows,Russo+:Haskell08,stefan:lio}, 
we prove this property by using the
\emph{term erasure} technique. The erasure function $\eraseName_L$
rewrites data at security levels that the attacker cannot observe into
the syntax node $\hole$.

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
  &|erase il (tconf id il' ie) =| \begin{cases}
    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
    |bullet| & |il' cantFlowTo il| \\
    |tconf id il' ie| & \text{otherwise}
  \end{cases} \\
  &|erase il emptyset = emptyset|\\
  &|erase il (iS [id mapsto Q]) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
    & \text{the label of thread |id|} \\
    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|
\end{align*}
\caption{
Erasure function for configurations, threads, system state, and
message queus.  In all other cases, |erasef il| is applied
homomorphically.
\label{fig:erasure}
}
\end{figure}

@@

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Using this definition, we can now expand the definition for the
specification family of languages.
%
Specifically, |specLang alpha (targetLang nop) = (ifc C, ifc V, .->,
erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and $|ifc V|
= |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the type for
tasks whose expressions have been reduced to values.\footnote{
Here, we abuse notation by using metavariables to describe types of
the corresponding non-terminals, e.g., |it| for the type of task.
}
%}

>>>>

\subsection{Security guarantees}
\label{sec:retrofit:formal}

In this section we present the formal security guarantees provided by
our embedding.
%
Concretely, we show that an IFC langauge, |specLang alpha (targetLang
nop)|, satisfies non-interference(NI)~\tocite{}.
%
Intuitively, non-interference states that secret values cannot be
leaked by programs written in the language.
%
As we show below, the precise scheduling policy |alpha| dictates
whether or not the guarantee holds for programs with diverging tasks.

We prove non-interference for |specLang alpha (targetLang nop)| using
the \emph{term erasure} technique of~\tocite{}.
%
Intuitively the term erasure technique allows us to show that a an
attacker does not learn any sensitive information from a program
written in a NI language, if the program behaves identically to the
same program with all sensitive data ``erased.''
% 
To accommodate for this, we extend our formalism to account for
programs with erased configurations and a function |erasef l| that
performs erasures, usually by rewriting (parts of) configurations that
are more sensitive than |l| to a new syntactic construct |bullet|.
%
Directly, we can now give a precise definition for the kinds of
languages we wish to prove NI.

@@

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Using this definition, |specLang alpha (targetLang nop) = (ifc C, ifc
V, .->, erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and
$|ifc V| = |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
%
Figure~\ref{fig:erasure} gives the precise definition for our erasure function.
%
%}

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
  &|fullconf id il' tS ie| \begin{cases}
    |bullet| & |il' cantFlowTo il| \\
    |fullconf id il' (erase l tS) (erase l ie)| & \text{otherwise}
  \end{cases} \\
  &|erase il emptyset = emptyset|\\
  &|erase il (iS [id mapsto Q]) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
    & \text{the label of thread |id|} \\
    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|
\end{align*}
\caption{
Erasure function for configurations, tasks, queue map, and message queues.
In all other cases, including target-language constructs, |erasef il| is
applied homomorphically.
\label{fig:erasure}
}
\end{figure}
